A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-19 manuscript.Rmd
describe the example research question earlier

We have structured the tutorial with a _learning by doing_ approach in mind, such that readers can follow along at their own computers.
We explicitly encourage readers to try out all R commands for themselves.
Unless stated otherwise, all code blocks are meant to be run in the statistical programming language R (tested with version `r with(R.version, paste0(major, ".", minor))`).

>>>>

We have structured the tutorial with a _learning by doing_ approach in mind, such that readers can follow along at their own computers.
We explicitly encourage readers to try out all R commands for themselves.
Unless stated otherwise, all code blocks are meant to be run in the statistical programming language R (tested with version `r with(R.version, paste0(major, ".", minor))`).
To guide the reader through all steps of a research project, we will use a exemplary research question:

> "Is there a mean difference in the personality trait 'Machiavellism' between genders?"

This example serves only didactic purposes and not to derive substantive claims.
Nevertheless, everything else is kept as close to a real research question as possible and we have preregistered the analysis without looking at the data beforehand and use actual data subsequently.
